Article Title

### 2024-04-30 paper/main.tex
add more details to outline, note potential images

\begin{itemize}
    \item Introduce the cosmology application - why is it important?  What type of data do we have?  What do we want to do with it?
    \item Review what has been done (Mira Titan, cosmic EMU, process convolutions?)
    \item Overview our contribution (two-fold, see below) and describe the layout of the manuscript
    \item Annie says: I would prefer not to have any section labelled "review", but rather to provide relevant review and citations as we go along.  Our contribution is in the folding together of many methods, not in proposing a true novel method, so I think this will flow more nicely.
    \item Provide the link to the github repository where all our codes are provided.
\end{itemize}

@@

Here, we provide further details on the form of the data (in the introduction, we only briefly introduce it).  Include a figure of the raw data for a particular cosmology.  We describe the different modeling components and the regions of the space where they are trusted.  We also describe how each cosmology is a simulation based on 8 inputs.

@@

@@

Here we can provide figures of the predicted mean and variances for a subset of the actual cosmologies.

@@

@@

Here we show results on held-out cosmologies.  We compare to cosmicEMU and Jared's convolution approach.

@@

>>>>

\begin{itemize}
    \item Introduce the cosmology application - why is it important?  What type of data do we have?  What do we want to do with it?
    \item Review what has been done (Mira Titan, cosmic EMU, process convolutions)
    \item Overview our contribution (two-fold, see below) and describe the layout of the manuscript
    \item Our contribution is in the synthesis of hierarchical modeling, DGPs, PCs.
    \item Provide the link to the github repository where all our codes are provided.
\end{itemize}

@@

Here, we provide further details on the form of the data (in the introduction, we only briefly introduce it).  Include a figure of the raw data for a particular cosmology.  We describe the different modeling components and the regions of the space where they are trusted.  We also describe how each cosmology is a simulation based on 8 inputs, and the output $\mathcal{P}(k)$ is functional.

@@

Images:
\begin{itemize}
    \item Example cosmology showing 16 low res, 1 high res, 1 pert, wt avg, and where each output is deemed unbiased
\end{itemize}

@@

Estimate one cosmology with 50,000 runs, and use this as a starting point for each of the others
Here we can provide figures of the predicted mean and variances for a subset of the actual cosmologies.

Images:
\begin{itemize}
    \item Illustration of DGP fit (post mean and UQ, could show cosmicEMU as well?)
    \item estimated warping (or, how all 111 warpings compare)
\end{itemize}

@@

\begin{itemize}
    \item show breakdown of estimated mean trend, basis functions/PCs, and weights of a particular PC/BF.
\end{itemize}

@@

Here we show results on held-out cosmologies.  We compare to cosmicEMU and Jared's convolution approach. We can also discuss estimation of main effects, interactions amongst the 8 parameters, and variance decomposition.

\begin{itemize}
    \item compare the 4 with boxplot: our DGP training, DGP testing, vs proc conv training (aka Jared's files), proc conv testing (aka Cosmic EMU)
    \item compare the 4's RMSEs as a function of $k$
    \item Main effects
\end{itemize}

@@

\section{Appendix}

The different appendices from dissertation as necessary. Can also put details of dataset in supplementary material.
